WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-05-28 article/Article.tex
more macro doc in the article
darcs-hash:20060528010302-2fc9d-dae3d7365571df125801e2cef260cfe17645ce15.gz

\begin{itemize}
  \item \verb$UNIQUE()$

  \item \verb$SORT()$

  \item \verb$INTERSECTION()$

  \item \verb$FILTER()$

  \item \verb$FILTER_DIMS()$

  \item \verb$INCREMENT()$

  \item \verb$DECREMENT()$

@@

  \item \verb$WRAP_IMAGE_FILTER_type(size)$ . \verb$type$ can be one of:
  \begin{itemize}
    \item \verb$INT$
    \item \verb$SIGN_INT$
    \item \verb$REAL$
    \item \verb$VECTOR_REAL$
    \item \verb$COV_VECTOR_REAL$
    \item \verb$RGB$
    \item \verb$ALL$
    \item \verb$SCALAR$
    \item \verb$VECTOR$
  \end{itemize}

>>>>

\begin{itemize}
  \item \verb$UNIQUE(var list)$ create a new list called \verb$var$ composed of the same
element than the ones in \verb$list$ without duplicate. This macro is useful to impose
a type even if it hasn't been selected by the user. The following line for example, from
\verb$Modules/IO/wrap_itkImageFileReader.cmake$, force the unsigned char type to be
wrapped:

\small \begin{verbatim}
  UNIQUE(image_types "UC;${WRAP_ITK_ALL_TYPES}")
\end{verbatim} \normalsize

  \item \verb$SORT(var list)$ create a new list called \verb$var$ which contains the
same elements than \verb$list$ sorted lexicographically

  \item \verb$INTERSECTION(var list1 list2)$ create a new list called \verb$var$ which
is the intersection of lists \verb$list1$ and \verb$list2$

  \item \verb$REMOVE(var list1 list2)$ Remove elements in \verb$list2$ from \verb$list1$
and store the result in \verb$var$

  \item \verb$INCREMENT(var number)$ increment \verb$number$ by one an store the result
in \verb$var$

  \item \verb$DECREMENT(var number)$ decrement \verb$number$ by one an store the result
in \verb$var$

  \item \verb$FILTER_DIMS(var dimension_condition)$ processes a \verb$dimension_condition$
and returns a list of the dimensions that (a) meet the condition, and (b) were selected
to be wrapped. Recall that the condition is either a CMake list of dimensions, or a
string of the form "n+" where n is a number.

@@

  \item \verb$WRAP_IMAGE_FILTER_type(size)$ . \verb$type$ can be one of:
  \begin{itemize}
    \item \verb$USIGN_INT$
    \item \verb$SIGN_INT$
    \item \verb$INT$
    \item \verb$REAL$
    \item \verb$VECTOR_REAL$
    \item \verb$COV_VECTOR_REAL$
    \item \verb$RGB$
    \item \verb$ALL$
    \item \verb$SCALAR$
    \item \verb$VECTOR$
  \end{itemize}
